Computing astrophysical inferences with diffusive nested sampling

### 2013-12-08 ms.tex
Product rule
Writing

\layoutstyle{8x11single}

@@

>>>>

\layoutstyle{8x11single}
\usepackage{amsmath}
\usepackage{dsfont}

\newcommand{\pars}{\boldsymbol{\theta}}
\newcommand{\data}{\mathbf{x}}

@@

A joint prior is assigned on the hypothesis space of possible $\pars$ values
and possible data sets $\data$:
\begin{eqnarray}
p(\pars, \data) = p(\pars) p(\data | \pars) = p(\data)p(\pars | \data)
\end{eqnarray}
The marginal distribution $p(\pars)$, which is usually called the ``prior'',
describes initial uncertainty about the value of the parameters. When the
data $\data$ becomes known, our state of knowledge about $\pars$ changes
from the marginal $p(\pars)$ to the conditional distribution $p(\pars | \data)$
that corresponds to the observed data, usually called the ``posterior''.
Incidentally, Bayesian inference can be understood as a special case of
MaxEnt updating, starting from the joint prior $p(\pars, \data)$ and applying
the constraint $P(\data = \data_{\rm actual}) = 1$ \citep{caticha}. Note that
this is not a ``derivation'' of Bayesian updating as the rules of probability
already imply a commitment to update to $p(\pars | \data)$ once $\data$ becomes
known (what else could a conditional probability be?).

\section{Probabilistic Catalogs}
The hypothesis space is the set of possible answers to the question
``how many objects are there, and what are their properties (positions, fluxes,
etc)''.

\section{Reverberation Mapping}
Many objects in the universe are too distant to resolve, so we cannot simply
``see'' what is going on. Rather we must infer what is going on. Active Galactic
Nuclei (AGN) are a good example.

\subsection{Models with known oversimplifications}
Computing the posterior $p(\pars | \data)$ would yield overconfident results
since the assumed model is known to be wrong. However certain parameters still
``exist'' (such as the black hole mass) and we want our posterior inferences
to be realistic.

We have been using the following subjective procedure. Later we give two
interpretations of this procedure which may lead the way to less subjective
approaches.
Using DNS we explore the mixture of constrained priors.
\begin{eqnarray}
p_{\rm DNS}(\theta) &=& \sum_{i=1}^n p(\theta)\mathds{1}\left[\mathcal{L} > L^*_i\right]
\end{eqnarray}
